\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

The development of Robotic and Autonomous Systems (RAS) requires rigorous testing methods to ensure reliability and safety in complex environments. While pure simulation offers rapid prototyping and physical experiments provide realistic validation, both approaches have significant limitations regarding fidelity or cost. Robot-in-the-Loop (RitL) testing bridges this gap by integrating physical robots into virtual simulation environments.

This thesis presents a novel Mixed Reality Environment designed to enhance RitL testing through the use of Digital Twins. Building upon the Virtual Environment for mobile Robotic Applications (VERA) framework, this work overcomes previous limitations in physical realism, scalability, and user interaction by leveraging a modern game engine integrated with the Robot Operating System 2 (ROS 2). The developed system creates a synchronized Digital Twin of the \textit{Educational Modular Autonomous Robot Osnabrück} (EMAROs) and provides immersive interfaces through Virtual Reality (VR) and Augmented Reality (AR) projection.

The system is validated through four distinct application scenarios—dynamic surface interaction, reactive physics, autonomous logistics, and smart farming—demonstrating its capability to facilitate real-time bidirectional interaction between the physical and virtual worlds. Performance benchmarks confirm that the architecture achieves low-latency synchronization (under 5 ms for AR) and supports complex environments with thousands of objects, offering a robust platform for the comprehensive evaluation of autonomous mobile robots.
\cite{NOT FINAL}